---
title: "Data Sources and Versioned Snapshots"
site: workflowr::wflow_site
output: workflowr::wflow_html
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

Exact reproduction uses the files committed under `data/raw/`, verified against
their SHA-256 manifest. Data providers may revise provisional counts, historical
records, schemas, or download URLs after the repository snapshot date. The
provider-access scripts therefore download current versions to a separate,
ignored directory and never silently replace the canonical inputs.

## Registered sources

```{r registered-sources, echo=FALSE}
sources <- utils::read.csv(
  here::here("config", "data_sources.csv"),
  stringsAsFactors = FALSE,
  check.names = FALSE
)
display_sources <- sources[c(
  "provider",
  "region",
  "frequency",
  "geography",
  "provider_identifier",
  "local_snapshot"
)]
names(display_sources) <- c(
  "Provider",
  "Region",
  "Frequency",
  "Geography",
  "Provider identifier",
  "Repository snapshot"
)
knitr::kable(display_sources)
```

## Snapshot verification

```{r snapshot-verification, eval=FALSE}
system2(
  "Rscript",
  c("--vanilla", "scripts/data_access/verify_snapshots.R")
)
```

```{r snapshot-summary, echo=FALSE}
manifest <- utils::read.csv(
  here::here("data", "raw", "manifest.csv"),
  stringsAsFactors = FALSE,
  check.names = FALSE
)
snapshot_summary <- aggregate(
  cbind(files = rep(1L, nrow(manifest)), bytes = manifest$bytes),
  by = list(provider = manifest$provider),
  FUN = sum
)
snapshot_summary$size_mb <- round(snapshot_summary$bytes / 1024^2, 1)
knitr::kable(
  snapshot_summary[c("provider", "files", "size_mb")],
  col.names = c("Provider", "Versioned files", "Size (MB)")
)
```

## Optional current-provider access

The scripts in
[`scripts/data_access`](https://github.com/AgueroZZ/covid_script/tree/main/scripts/data_access)
document how to retrieve current provider versions where automated access is
available. CDC WONDER exports require acceptance of the provider's data-use terms
and are retained as saved query exports. Source-specific details are recorded in
[`documentation/data-sources.md`](https://github.com/AgueroZZ/covid_script/blob/main/documentation/data-sources.md).
