---
title: "Reproduce the Analysis"
site: workflowr::wflow_site
output: workflowr::wflow_html
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

## 1. Restore the software environment

Run all commands from the repository root.

```{r restore-environment, eval=FALSE}
renv::restore()
```

## 2. Verify inputs and tests

```{r verify-repository, eval=FALSE}
system2(
  "Rscript",
  c("--vanilla", "scripts/data_access/verify_snapshots.R")
)
system2("Rscript", c("--vanilla", "tests/testthat.R"))
```

The first command verifies file sizes and SHA-256 hashes for the exact source
snapshots used by the analysis.

## 3. Inspect analysis inventories

The following commands validate source-specific preprocessing and construct
manifests without fitting models:

```{r inspect-inventories, eval=FALSE}
system2(
  "Rscript",
  c(
    "--vanilla",
    "scripts/model_fitting/europe/refit_eurostat.R",
    "--manifest-only=true"
  )
)
system2(
  "Rscript",
  c(
    "--vanilla",
    "scripts/model_fitting/england_wales/refit.R",
    "--manifest-only=true"
  )
)
system2(
  "Rscript",
  c(
    "--vanilla",
    "scripts/model_fitting/ireland/refit.R",
    "--manifest-only=true"
  )
)
system2(
  "Rscript",
  c(
    "--vanilla",
    "scripts/model_fitting/canada/refit.R",
    "--manifest-only=true"
  )
)
```

## 4. Fit models only when required

Regional runners fit models when `--manifest-only=true` is omitted. The United
States target graph is started with:

```{r fit-models, eval=FALSE}
system2(
  "Rscript",
  c("--vanilla", "scripts/pipeline/run_pipeline.R")
)
```

These computations may require substantial memory and wall time. They write
fitted objects and posterior draws below the ignored `output/` directory and are
not part of website generation.

## 5. Construct publication outputs

After the required standardized summaries are present locally:

```{r construct-publication-outputs, eval=FALSE}
system2(
  "Rscript",
  c(
    "--vanilla",
    "scripts/reporting/run_all.R",
    "--include_caption_review=true",
    "--strict=true"
  )
)
```

Figures are written as editable PDF and 300-dpi PNG files. Table 1 is written as
CSV and HTML. A completed, validated release freeze can then be synchronized to
the tracked publication directories.

## 6. Build the website

```{r build-site, eval=FALSE}
system2(
  "Rscript",
  c("--vanilla", "scripts/publication/build_site.R")
)
```

This final command verifies the tracked artifact hashes and builds the website
directly from those files. It does not read fitted model objects or posterior
draws.
