---
title: "Reproduce the Analysis"
site: workflowr::wflow_site
output: workflowr::wflow_html
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

## 1. Restore the software environment

Run all commands from the repository root.

```{r restore-environment, eval=FALSE}
renv::restore()
```

## 2. Verify inputs and tests

```{r verify-repository, eval=FALSE}
system2(
  "Rscript",
  "scripts/data_access/verify_snapshots.R"
)
system2("Rscript", "tests/testthat.R")
```

The first command verifies file sizes and SHA-256 hashes for the exact source
snapshots used by the analysis.

## 3. Inspect analysis inventories

The following commands validate source-specific preprocessing and construct
manifests without fitting models:

```{r inspect-inventories, eval=FALSE}
system2(
  "Rscript",
  c(
    "scripts/model_fitting/europe/refit_eurostat.R",
    "--manifest-only=true"
  )
)
system2(
  "Rscript",
  c(
    "scripts/model_fitting/england_wales/refit.R",
    "--manifest-only=true"
  )
)
system2(
  "Rscript",
  c(
    "scripts/model_fitting/ireland/refit.R",
    "--manifest-only=true"
  )
)
system2(
  "Rscript",
  c(
    "scripts/model_fitting/canada/refit.R",
    "--manifest-only=true"
  )
)
```

## 4. Fit models only when required

Regional runners fit models when `--manifest-only=true` is omitted. The United
States target graph is started with:

```{r fit-models, eval=FALSE}
system2(
  "Rscript",
  "scripts/pipeline/run_pipeline.R"
)
```

These computations may require substantial memory and wall time. They write
fitted objects and posterior draws below the ignored `output/` directory and are
not part of website generation.

## 5. Use or prepare precomputed fitted results

Canonical fitted objects are distributed separately from Git because model
fitting is computationally intensive. A checksum-verified Zenodo package can be
prepared from the completed local analysis without rerunning any model:

```{r zenodo-deposit, eval=FALSE}
system2(
  "Rscript",
  "scripts/submission/prepare_zenodo_deposit.R"
)
```

The package retains final production fits, compact diagnostics, reporting
inputs, configuration, and provenance. Validation duplicates, compiler
products, failed runs, stale freezes, and private manuscript files are
excluded. The DOI is added after creator metadata, license, and the article
relationship are confirmed.

## 6. Construct publication outputs

After the required standardized summaries are present locally:

```{r construct-publication-outputs, eval=FALSE}
system2(
  "Rscript",
  c(
    "scripts/reporting/run_all.R",
    "--include_caption_review=true",
    "--strict=true"
  )
)
```

Figures are written as editable PDF and 300-dpi PNG files. Table 1 is written as
CSV and HTML. A completed, validated release freeze can then be synchronized to
the tracked publication directories.

## 7. Build the website

```{r build-site, eval=FALSE}
system2(
  "Rscript",
  "scripts/publication/build_site.R"
)
```

This final command verifies the tracked artifact hashes and builds the website
directly from those files. It does not read fitted model objects or posterior
draws.
