---
title: "Supplementary Analyses"
site: workflowr::wflow_site
output: workflowr::wflow_html
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

The supplementary workflow contains many region-, age-, sex-, wave-, and
diagnostic-specific outputs. To keep this website concise, the complete set is
not embedded here. The commands below reproduce the analysis inventories and
reporting outputs, and the lightweight examples demonstrate the tracked input
and result contracts.

## Reproduction commands

Verify every versioned source file before analysis:

```{r verify-snapshots, eval=FALSE}
system2(
  "Rscript",
  "scripts/data_access/verify_snapshots.R"
)
```

Inspect regional model inventories without fitting models:

```{r model-inventories, eval=FALSE}
commands <- c(
  "scripts/model_fitting/europe/refit_eurostat.R",
  "scripts/model_fitting/england_wales/refit.R",
  "scripts/model_fitting/ireland/refit.R",
  "scripts/model_fitting/canada/refit.R"
)
lapply(commands, function(script) {
  system2("Rscript", c(script, "--manifest-only=true"))
})
```

After completed model summaries have been written locally, reconstruct all
registered manuscript outputs:

```{r reporting-outputs, eval=FALSE}
system2(
  "Rscript",
  c(
    "scripts/reporting/run_all.R",
    "--include_caption_review=true",
    "--strict=true"
  )
)
```

## Example 1: versioned source inventory

```{r source-inventory, echo=TRUE}
raw_manifest <- utils::read.csv(
  here::here("data", "raw", "manifest.csv"),
  stringsAsFactors = FALSE,
  check.names = FALSE
)
source_inventory <- aggregate(
  cbind(files = rep(1L, nrow(raw_manifest)), bytes = raw_manifest$bytes),
  by = list(provider = raw_manifest$provider),
  FUN = sum
)
source_inventory$size_mb <- round(source_inventory$bytes / 1024^2, 1)
knitr::kable(
  source_inventory[c("provider", "files", "size_mb")],
  col.names = c("Provider", "Files", "Size (MB)")
)
```

## Example 2: publication-table preview

```{r table-preview, echo=TRUE}
table_01 <- utils::read.csv(
  here::here("tables", "manuscript", "table_01_wave_pscores.csv"),
  check.names = FALSE
)
knitr::kable(utils::head(table_01, 6L))
```

Complete output remains available through the same scripts and local `output/`
tree; the website does not use those local files as build inputs.
