---
title: "Supplementary Analyses"
site: workflowr::wflow_site
output: workflowr::wflow_html
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

The frozen supplementary bundle presents every cohort in the current analysis
contract without loading fitted models in the browser. It contains 1,119
registered geography-by-age-by-sex analyses: 1,118 successful compact
posterior-predictive results and one explicitly retained historical model
failure.

## Interactive exploration

| Explorer | Available selections | Output |
|:--|:--|:--|
| [Time series and pointwise P-scores](supplementary_timeseries.html) | Analysis family, geography, age group, sex, and display metric | Observed mortality, expected mortality with a 95% posterior predictive interval, or the pointwise P-score curve |
| [Wave-specific maps](supplementary_wave_maps.html) | Region, age group, sex, Initial/Alpha/Delta/Omicron wave, and posterior summary | Interactive geographic P-score or excess-death maps with exact values in an accessible table |
| [Vaccination-group trajectories](supplementary_vaccination_groups.html) | P-score or female-minus-male P-score difference, Europe or United States, original age group, two vaccination thresholds, and manual location membership | Recomputed low- and high-vaccination trajectories with panel-specific coverage screening, manuscript presets, uncertainty intervals, and downloadable current membership |

The pages load only the shard required by the current selection. They therefore
remain static GitHub Pages files rather than a server process, while still
exposing the full registered stratification set. The vaccination explorer adds
approximately 25 MB of summary-only browser assets; fitted objects remain local.

## Frozen scope

| Analysis family | Registered cohorts | Time scale |
|:--|--:|:--|
| Eurostat Europe | 388 | Weekly |
| United States, non-sex-stratified | 204 | Monthly |
| United States, sex-stratified | 408 | Monthly |
| Canada, non-sex-stratified | 40 | Weekly |
| Canada, sex-stratified | 72 | Weekly |
| England and Wales | 3 | Weekly |
| Republic of Ireland | 4 | Quarterly |

The United States branch `Vermont / 0-44 / female` is retained in the registry
with status `model_failed`; no value is imputed. Superseded Europe,
England-and-Wales, and Ireland model batches, and unregistered United States
`age_all` files, are not mixed into this frozen analysis contract.

## Summary definitions

For each successful cohort, the bundle records observed deaths, the expected
posterior mean and median, the central 95% posterior predictive interval, and
the pointwise P-score distribution. Interactive mortality charts use the
posterior median as their center line. This matters for a small number of sparse
cohorts where extreme posterior draws can pull the mean outside the central
interval; the downloadable table retains both summaries without truncation.

Wave summaries use the four half-open intervals fixed in `config/analysis.yml`:

- Initial: March 1, 2020 to November 1, 2020;
- Alpha: November 1, 2020 to July 1, 2021;
- Delta: July 1, 2021 to January 1, 2022;
- Omicron: January 1, 2022 to April 1, 2024.

For a wave with observed periods, the wave P-score is computed draw by draw as

\[
P = \frac{\sum_t Y_t - \sum_t E_t}{\sum_t E_t},
\]

before posterior quantiles are taken. It is not an average of pointwise
P-scores.

## Downloads

- [Registered cohort inventory](assets/supplementary/downloads/registry.csv)
- [Complete pointwise summaries (compressed CSV)](assets/supplementary/downloads/pointwise.csv.gz)
- [Four-wave summaries](assets/supplementary/downloads/wave_summary.csv)
- [Compact prediction source hashes](assets/supplementary/downloads/source_inventory.csv)
- [Canonical observed-data source hashes](assets/supplementary/downloads/observed_source_inventory.csv)
- [Bundle metadata and input hashes](assets/supplementary/downloads/bundle_metadata.yml)
- [Vaccination coverage for analysis geographies](assets/supplementary/vaccination_groups/downloads/vaccination_membership.csv)
- [Manuscript membership presets for vaccination-group analyses](assets/supplementary/vaccination_groups/downloads/manuscript_membership.csv)
- [Panel-specific usable-observation coverage](assets/supplementary/vaccination_groups/downloads/coverage.csv)
- [Vaccination explorer geography summaries (compressed CSV)](assets/supplementary/vaccination_groups/downloads/geography_summaries.csv.gz)
- [Vaccination explorer availability records](assets/supplementary/vaccination_groups/downloads/availability.csv)
- [Vaccination explorer metadata](assets/supplementary/vaccination_groups/downloads/bundle_metadata.yml)

The public files contain summary statistics only. Posterior draw matrices and
fitted model objects are not included.

## Rebuild command

The bundle is derived from the registered observed-data snapshots and existing
compact posterior-predictive objects. It does not refit a model.

```{r rebuild-supplementary, eval=FALSE}
system2(
  "Rscript",
  "scripts/supplementary/build_bundle.R"
)
system2(
  "Rscript",
  "scripts/supplementary/build_vaccination_groups.R"
)
```
